Federated Learning's Blessing:\\ FedAvg has Linear Speedup

### 2020-09-16 source-iclr/app_sgd_scvx_smooth.tex
proof th1 minor

% !TEX ROOT=./supp-main.tex
To facilitate reading, theorems from the main paper are restated and numbered identically. We first summarize some properties of $L$-smooth and $\mu$-strongly
convex functions~\cite{rockafellar1970convex}. 
\begin{lemma}
	Let $F$ be a convex $L$-smooth function. Then we have the following
	inequalities:

	1. Quadratic upper bound: $0\leq F(\vw)-F(\vw')-\langle\nabla F(\vw'),\vw-\vw'\rangle\leq\frac{L}{2}\|\vw-\vw'\|^{2}$.

	2. Coercivity: $\frac{1}{L}\|\nabla F(\vw)-\nabla F(\vw')\|^{2}\leq\langle\nabla F(\vw)-\nabla F(\vw'),\vw-\vw'\rangle$.

	3. Lower bound: $F(\vw)\geq F(\vw')+\langle\nabla F(\vw'),\vw-\vw'\rangle+\frac{1}{2L}\|\nabla F(\vw)-\nabla F(\vw')\|^{2}$.
	In particular, $\|\nabla F(\vw)\|^{2}\leq2L(F(\vw)-F(\vw^{\ast}))$.

	4. Optimality gap: $F(\vw)-F(\vw^{\ast})\leq$$\langle\nabla F(\vw),\vw-\vw^{\ast}\rangle$.
\end{lemma}
%
\begin{lemma}
	Let $F$ be a $\mu$-strongly convex function. Then 
	\begin{align*}
	F(\vw) & \leq F(\vw')+\langle\nabla F(\vw'),\vw-\vw'\rangle+\frac{1}{2\mu}\|\nabla F(\vw)-\nabla F(\vw')\|^{2}\\
	F(\vw)-F(\vw^{\ast}) & \leq\frac{1}{2\mu}\|\nabla F(\vw)\|^{2}
	\end{align*}
\end{lemma}

>>>>

% !TEX ROOT=./supp-main.tex
